An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2021-12-29 simplified_sdc_intro/paper.tex
more figures

Zoom panels showing different runs

For supernova calculations, we often want to know how much mass of
\isot{Ni}{56} was produced.  Table \ref{table:masses} shows the total
mass of \isot{He}{4}, \isot{Si}{28}, and \isot{Ni}{56} for each of the
simulations.

>>>>

We next look at how the structure seen in
Figures~\ref{fig:subch_strang_cfl08_I} and \ref{fig:subch_sdc_cfl08_I}
vary with CFL number and network tolerance.  We focus just on the
region behind the inward propagating shock.
Figures~\ref{fig:strang_enuc_summary} and
\ref{fig:strang_abar_summary} show the nuclear energy generation rate
and mean molecular weight for all of the Strang runs.  We see that
changing the CFL number does little to affect the state behind the
shock---it continues to take on the mottled appearance characteristic
of not reaching a proper equilibrium.  For the {\tt mixedtol} case, we
see that the state is greatly improved.  We were unable to run the
{\tt tol1.e-6} case for Strang, as the code aborted with too many
subcycles.  While reducing the tolerances does help, it greatly
increases the cost of the simulation.

\begin{figure}
\plotone{strang_enuc_summary_plot.pdf}
\caption{\label{fig:strang_enuc_summary} Comparison of Strang runs showing
the nuclear energy generation rate behind the inward propagating
shock.}
\end{figure}

\begin{figure}
\plotone{strang_abar_summary_plot.pdf}
\caption{\label{fig:strang_abar_summary} Comparison of Strang runs showing
the mean molecular weight behind the inward propagating
shock.}
\end{figure}

The SDC comparisons are shown in Figures~\ref{fig:sdc_enuc_summary}
and \ref{fig:sdc_abar_summary}.  We see that the state behind the
shock looks great regardless of the CFL or integrator tolerances.

\begin{figure}
\plotone{sdc_enuc_summary_plot.pdf}
\caption{\label{fig:sdc_enuc_summary} Comparison of simplified-SDC runs showing
the nuclear energy generation rate behind the inward propagating
shock.}
\end{figure}

\begin{figure}
\plotone{sdc_abar_summary_plot.pdf}
\caption{\label{fig:sdc_abar_summary} Comparison of simplified-SDC runs showing
the mean molecular weight behind the inward propagating
shock.}
\end{figure}

To quantify this effect, we next looks at the total mass of some key species.
This is often a desired diagnostic for supernova calculations, since 
\isot{Ni}{56} powers the lightcurve.  Table \ref{table:masses} shows the total
mass of \isot{He}{4}, \isot{Si}{28}, and \isot{Ni}{56} for each of the
simulations.
